Brownian Dynein Model

### 2015-08-22 latex/derivation.tex
Finish re-derivation of angular velocity matrix equation terms.

Our goal is to take the above system of equations and put it in this form:

@@

where $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s. We accomplish this by taking the above system of equations, equating terms with equal lambda terms to eliminate lambdas, and rearranging.

\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
Here we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$

@@

@@

@@

@@

@@

@@

@@

@@

\begin{align}
  A_1 &= -4L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{bl}) + \cos(\Theta_{bl})\cos(\Theta_{bl})\Big)\\
  A_2 &= -3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\\
  A_3 &= 2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{bl}) + \cos(\Theta_{mr})\cos(\Theta_{bl})\Big)\\
  A_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{bl}) + \cos(\Theta_{br})\cos(\Theta_{bl})\Big)\\
  X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))+\\
      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))\\
\end{align}

@@

\begin{multline}
-\frac{1}{\gamma}\lambda_{lt} =
\Big(\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big) \frac{1}{(Y_{t } - Y_{ml})}
\end{multline}

@@

\begin{align}
  C_1 &= - 2L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{mr}) + \cos(\Theta_{bl})\cos(\Theta_{mr})\Big) \\
  C_2 &= - 2L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{mr}) + \cos(\Theta_{ml})\cos(\Theta_{mr})\Big) \\
  C_3 &= 2L_{t} \\
  C_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big) \\
  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr}) + \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr}
+ \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr}) \\
\end{align}

@@

\section{Breaking terms down into symbols}

\begin{multline}
  X_1 = \frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{s}} + \frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{s}} \\
\end{multline}

\begin{multline}
  X_2 = \mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{t}\gamma} + \\
  \mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{t}}
\end{multline}

\begin{multline}
  X_3 = \mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
	\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
\end{multline}
The following is David's simplification of $X_3$:
\begin{align}
  X_3 &= -\frac{1}{L_s}\left\{ \sin(\Theta_{ml})\left(\frac{F_{xt}+F_{xmr}+F_{xbr}}{\gamma} + R_{xt }+R_{xmr}+R_{xbr}\right) -
    \cos(\Theta_{ml})\left(\frac{F_{yt }+F_{ymr}+F_{ybr}}{\gamma} +
    R_{yt}+R_{ymr}+R_{ybr}\right) \right\}
    \\
    &?= \frac{\hat{a}_{ml}\cdot \vec{F}_{tot_{ml}}}{\gamma L_s}
\end{align}
where $\hat a$ is a unit vector in a the direction related to the $ml$
segment, and $\vec{F}_{tot_{ml}}$ is a total force of some sort,
including the random fluctuations.  I don't think we want to write the
formula in this final way, but it may help in thinking about the
equations.  I certainly think that the form with just one $\sin$ and
one $\cos$ is an improvement, and reduces the likelihood of
introducing sign errors (or sine errors, for that matter).

\begin{multline}
  X_4 = \mn \frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}
  {\gamma L_t} \\+ \mn \frac{\sin(\Theta_{bl})R_{xml} +\mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t} \\
\end{multline}

\section{System solution!}
This system is solved via Mathematica...\\
\begin{multline}
N_{bl} =
(-B_2 C_4 D_3 X_1 + B_2 C_3 D_4 X_1 + A_4 C_3 D_2 X_2 - A_3 C_4 D_2 X_2 - A_4 C_2 D_3 X_2 + A_2 C_4 D_3 X_2 +\\
 A_3 C_2 D_4 X_2 - A_2 C_3 D_4 X_2 + A_4 B_2 D_3 X_3 - A_3 B_2 D_4 X_3 - A_4 B_2 C_3 X_4 + A_3 B_2 C_4 X_4 +\\
B_4 (-C_3 D_2 X_1 + C_2 D_3 X_1 + A_3 D_2 X_3 - A_2 D_3 X_3 - A_3 C_2 X_4 + A_2 C_3 X_4) + B_3 (C_4 D_2 X_1 - \\
C_2 D_4 X_1 - A_4 D_2 X_3 + A_2 D_4 X_3 + A_4 C_2 X_4 - A_2 C_4 X_4)) \\
\end{multline}

>>>>

Our goal is to take the above system of equations and put it in matrix form:

@@

This will allow us to perform a matrix solution for the angular velocities. $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s. The above system of equations has four lambda terms: $\lambda_{ls}, \lambda_{lt}, \lambda_{rt}$ and $\lambda_{ls}$. Each term is present in two equations. We will use this redundancy to eliminate the lambda terms and create the above matrix.

\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$\\

We start by dividing out the position terms in Equations (\ref{eq:Ax}) and (\ref{eq:Ay}) to make their LHSs identical.

@@

We then equate them.

@@

Then we group like terms for clarity.

@@

We then expand all the $\dot{X}$ terms using their definitions from the Cartesian Velocities section above.

@@

Then we group together the like terms from the expansion.

@@

We then bring all the angular velocity terms to one side and all the force terms to the other side.

@@

We then distribute the $L_s\sin(\Theta_{bl})$ and $L_s\cos(\Theta_{bl})$ terms into the expression.

@@

Finally, we group all terms by their angular velocity.

@@

This is the form we want. We now know the value of $A_1, A_2, A_3, A_4$ and $X_1$.

\begin{align}
  A_1 &= -4L_{s}\\
  A_2 &= -3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{bl}) + \cos(\Theta_{ml})\cos(\Theta_{bl})\Big)\\
  A_3 &= 2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{bl}) + \cos(\Theta_{mr})\cos(\Theta_{bl})\Big)\\
  A_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{bl}) + \cos(\Theta_{br})\cos(\Theta_{bl})\Big)\\
  X_1 &= \Big(- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{bl}))+\\
      &+ \Big( \frac{1}{\gamma}F_{xml} + \frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xml} + R_{xt } + R_{xmr} + R_{xbr} \Big)(\sin(\Theta_{bl}))
\end{align}

@@

\begin{multline}
-\frac{1}{\gamma}\lambda_{lt} =
\Big(
\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yt} - R_{ymr} - R_{ybr}\Big) \frac{1}{(Y_{t } - Y_{ml})}
\end{multline}

\begin{multline}
\Big(
\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xt } - R_{xmr} - R_{xbr}\Big)(Y_{t } - Y_{ml}) =\\
\Big(
\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yt} - R_{ymr} - R_{ybr}\Big)(X_{t } - X_{ml})
\end{multline}

\begin{multline}
\Big(
\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml})) =\\
\Big(
\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
\end{multline}

\begin{multline}
\Big(\dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr}
- L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
- \Big(\dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr} 
+ L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
\end{multline}

\begin{multline}
\Big( -3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
+ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
- \Big( 3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} -2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
- L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
- \Big(-\frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
\end{multline}

\begin{multline}
\Big( -3L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}
+ L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\sin(\Theta_{ml}))\\
+ \Big(-3L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}
+ L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}\Big)(L_t\cos(\Theta_{ml})) =\\
\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
\end{multline}

\begin{multline}
\Big( -3L_{s}\sin(\Theta_{bl})L_t\sin(\Theta_{ml})\dot{\Theta}_{bl} - 3L_{t}\sin(\Theta_{ml})L_t\sin(\Theta_{ml})\dot{\Theta}_{ml}
+ 2L_{t}\sin(\Theta_{mr})L_t\sin(\Theta_{ml})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})L_t\sin(\Theta_{ml})\dot{\Theta}_{br}\Big)\\
+ \Big(-3L_{s}\cos(\Theta_{bl})L_t\cos(\Theta_{ml})\dot{\Theta}_{bl} - 3L_{t}\cos(\Theta_{ml})L_t\cos(\Theta_{ml})\dot{\Theta}_{ml}
+ 2L_{t}\cos(\Theta_{mr})L_t\cos(\Theta_{ml})\dot{\Theta}_{mr} + L_{s}\cos(\Theta_{br})L_t\cos(\Theta_{ml})\dot{\Theta}_{br}\Big) =\\
\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_t\cos(\Theta_{ml}))
+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(L_t\sin(\Theta_{ml}))
\end{multline}

\begin{multline}
-3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\dot{\Theta}_{bl}
-3L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{ml}) + \cos(\Theta_{ml})\cos(\Theta_{ml})\Big)\dot{\Theta}_{ml}\\
+2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\dot{\Theta}_{mr}
+ L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\dot{\Theta}_{br} =\\
\Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))
+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
\end{multline}

\begin{align}
  C_1 &= -3L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{ml}) + \cos(\Theta_{bl})\cos(\Theta_{ml})\Big)\\
  C_2 &= -3L_{t}\\
  C_3 &= +2L_{t}\Big(\sin(\Theta_{mr})\sin(\Theta_{ml}) + \cos(\Theta_{mr})\cos(\Theta_{ml})\Big)\\
  C_4 &= + L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{ml}) + \cos(\Theta_{br})\cos(\Theta_{ml})\Big)\\
  X_3 &= \Big(-\frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr}\Big)(\cos(\Theta_{ml}))\\
      &+ \Big(\frac{1}{\gamma}F_{xt } + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr} + R_{xt } + R_{xmr} + R_{xbr}\Big)(\sin(\Theta_{ml}))
\end{align}

@@

\begin{align}
  C_1 &= - 2L_{s}\Big(\sin(\Theta_{bl})\sin(\Theta_{mr}) + \cos(\Theta_{bl})\cos(\Theta_{mr})\Big) \\
  C_2 &= - 2L_{t}\Big(\sin(\Theta_{ml})\sin(\Theta_{mr}) + \cos(\Theta_{ml})\cos(\Theta_{mr})\Big) \\
  C_3 &= 2L_{t} \\
  C_4 &= L_{s}\Big(\sin(\Theta_{br})\sin(\Theta_{mr}) + \cos(\Theta_{br})\cos(\Theta_{mr})\Big) \\
  X_3 &= \Big(-R_{ymr} -R_{ybr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}\Big)\cos(\Theta_{mr})\\
      &+ \Big(R_{xmr} + R_{xbr} + \frac{1}{\gamma}F_{xmr} + \frac{1}{\gamma}F_{xbr}\Big)\sin(\Theta_{mr})
\end{align}

@@

\section{CAS solution to Matrix Equation}

We now have our equations in the following form:

\begin{equation}
  \begin{pmatrix}
    A_1 & A_2 & A_3 & A_4 \\
    B_1 & B_2 & B_3 & B_4 \\
    C_1 & C_2 & C_3 & C_4 \\
    D_1 & D_2 & D_3 & D_4 \\    
  \end{pmatrix}
\times
  \begin{pmatrix}
    \Theta_{bl} \\
    \Theta_{ml} \\
    \Theta_{mr} \\
    \Theta_{br} \\
  \end{pmatrix}
=
  \begin{pmatrix}
    X_1 \\
    X_2 \\
    X_3 \\
    X_4 \\
  \end{pmatrix}
\end{equation}

We use a CAS (Mathematica) to solve this equation for the angular velocities. We arrive at the following expressions, which we have broken up into numerator and denominator for legibility:

\begin{multline}
N_{bl} =
(-B_2 C_4 D_3 X_1 + B_2 C_3 D_4 X_1 + A_4 C_3 D_2 X_2 - A_3 C_4 D_2 X_2 - A_4 C_2 D_3 X_2 + A_2 C_4 D_3 X_2 +\\
 A_3 C_2 D_4 X_2 - A_2 C_3 D_4 X_2 + A_4 B_2 D_3 X_3 - A_3 B_2 D_4 X_3 - A_4 B_2 C_3 X_4 + A_3 B_2 C_4 X_4 +\\
B_4 (-C_3 D_2 X_1 + C_2 D_3 X_1 + A_3 D_2 X_3 - A_2 D_3 X_3 - A_3 C_2 X_4 + A_2 C_3 X_4) + B_3 (C_4 D_2 X_1 - \\
C_2 D_4 X_1 - A_4 D_2 X_3 + A_2 D_4 X_3 + A_4 C_2 X_4 - A_2 C_4 X_4)) \\
\end{multline}
